The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-06 paper.tex
update

\section{Results}

@@

\label{Results}
  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The slices of pressure (top), temperature (middle), and number density (bottom)\
             at the end of simulation $t=12.39$ Myr.\
             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
             for a duration $t=0$--$1.2$ Myr.\
             Comparison between the clumpy (first column from left)\
             and the smooth disc (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
             Also, the two rightmost columns reveal that the development of the innermost bubbles (dashed box)\
             is always associated with the disc, and without the disc,\
             the outermost bubbles and the turbulent region will be tilted,
             indicating the dense disc is crucial for\
             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

  \subsection{X-ray}
  The X-ray emissivity in an energy range 0.6 -- 1.0 keV is calculated\
  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\

  Note that the observed X-ray emission is contributed by all the gas in the Milky Way halo,\
  which likely extends to a radius of $\sim$250 kpc \citep{halo-radius-1,halo-radius-2},\
  much bigger than our simulation box. Therefore, we first compute the X-ray emissivity\
  from the simulated gas within a radius of 25 kpc away from the GC.
  Then, beyond 25 kpc the gas is assumed to be isothermal with $T=10^6$ K and\
  follows out to a radius of 250 kpc the observed density profile of \citep{temperature-MW}.

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range.\
               Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
               and observed from the solar system.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disc normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}

>>>>

\section{Results}
\label{Results}

\subsection{Morphology}

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The slices of pressure (top), temperature (middle), and number density (bottom)\
             at the end of simulation $t=12.39$ Myr.\
             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
             for a duration $t=0$--$1.2$ Myr.\
             Comparison between the clumpy (first column from left)\
             and the smooth disc (second) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
             in an uniform atmosphere (third) is spherical-shape,\
             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
             Also, the two rightmost columns reveal that the development of the innermost bubbles (dashed box)\
             is always associated with the disc, and without the disc,\
             the outermost bubbles and the turbulent region will be tilted,
             indicating the dense disc is crucial for\
             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disc-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

  \subsection{X-ray}
  The X-ray emissivity in an energy range 0.6 -- 1.0 keV is computed\
  for each computational volume cell
  using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
  implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\
  The X-ray intensity map are then generated by projecting the emissivities\
  along lines of sight across the sky.

  We point out that the projections employed throughout this paper is \lq perspective\rq,\
  which has the effect of making distant object appear smaller than the same object in the near distance,\
  and also that the observed X-ray emission is contributed by all the gas in the Milky Way halo,\
  which likely extends to a radius of $\sim$250 kpc \citep{halo-radius-1,halo-radius-2},\
  much bigger than our simulation box. Therefore, we first compute the X-ray emissivity\
  from the simulated gas within a radius of 25 kpc away from the GC.
  Then, beyond 25 kpc the gas is assumed to be isothermal with $T=10^6$ K and\
  follows out to a radius of 250 kpc the observed density profile of \citep{temperature-MW}.

  \Cref{fig__xray_0.8keV_angle_000} shows the projected X-ray emissivity from simulation,\
  overlaid with the red arrow representing the direction of the bipolar jet,\
  constantly ejecting during 0--1.2 Myr at an angle of $45^{\circ}$\
  to the disc normal.

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range.\
               Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center using a Hammer-Aitoff projection,\
               and observed from the solar system.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disc normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray-map}
  \end{figure*}
